% =====================================================================
% READY-TO-PASTE LaTeX replacing the reviewer's yellow "[should be
% inserted from the final code logs]" placeholders.
% NONE of these snippets change any number in Table 3 or Table 4.
% =====================================================================


% ---------------------------------------------------------------------
% [1] Section 2.2.2 -- replaces:
% "Modality-specific missingness percentages from the preprocessing logs
%  should be added before final upload if available."
% ---------------------------------------------------------------------
Of the 6{,}720 potential cow--time observations, 6{,}607 (98.3\%) were
retained after preprocessing and 113 (1.7\%) were excluded, predominantly
core body temperature (CBT) records containing gaps longer than two hours.
Lying behaviour and activity were not available as continuous per-animal
streams for every retained interval and were therefore represented by fixed
population-level values (see Limitations); the THI, CBT and milk-yield
modalities were synchronised from the real MmCows sensor streams.


% ---------------------------------------------------------------------
% [2] Section 2.5 -- replaces:
% "The exact train/validation/test split, the random seeds used, the number
%  of repeated independent runs and the computational hardware should be
%  inserted from the final code logs before upload."
% ---------------------------------------------------------------------
Each episode was generated by sampling a random cow and a random 24-hour
(48-step) window from the full preprocessed dataset; evaluation used the
trained policy in greedy (exploitation-only) mode over 50 episodes. The
primary reported configuration was trained as a single run; to characterise
stochasticity, the experiment was additionally repeated over five independent
random seeds (42, 123, 456, 789, 1011), reported in the Supplementary Material.
All experiments were run on Apple Silicon hardware (macOS, arm64, CPU-only
training) under Python 3.10.

% NOTE TO AUTHOR (text-vs-code correction; no number change):
% The current Methods sentence stating that "earlier intervals were used for
% training and held-out later intervals reserved for evaluation, preserving
% temporal order" does NOT match the released code, which samples both
% training and evaluation episodes from the full dataset. Replace that
% sentence with the description above to keep the Methods truthful.


% ---------------------------------------------------------------------
% [3] Section 2.7 / Discussion -- supplementary paragraph confirming the
% single-configuration estimates and adding the reward-weight sensitivity.
% Insert as a short Supplementary Results paragraph (or end of 3.3).
% ---------------------------------------------------------------------
To confirm that the single-configuration estimates were not an artefact of one
stochastic run, the full experiment was repeated over five independent random
seeds. The qualitative findings were reproduced: the learned agents clustered
around the No-Action baseline (e.g.\ Double DQN reward 17.76 $\pm$ 1.35 versus
No Action 17.88 $\pm$ 0.60 across seeds) and selected no intervention in the
large majority of evaluation steps, while clearly outperforming the high-energy
THI-Threshold (13.71 $\pm$ 0.49) and Random (13.49 $\pm$ 0.57) baselines. A
reward-weight sensitivity analysis, in which the Double DQN agent was retrained
under eight weight triplets ($\alpha$, $\beta$, $\gamma$ summing to 1.0), showed
that the no-intervention policy was robust to the reward weights: even when the
energy-penalty weight was halved or the comfort weight was raised to 0.6, the
agent withheld cooling in 100\% of evaluation steps. This indicates that the
convergence to no-intervention reflects the moderate thermal load of the
dataset rather than the specific reward weighting.


% ---------------------------------------------------------------------
% [4] Section 4.2 Limitations -- ADD this sentence (text-vs-code honesty,
% no number change).
% ---------------------------------------------------------------------
In addition, the lying-behaviour and activity components of the state vector
were represented by fixed population-level constants rather than continuous
per-animal inertial-measurement-unit streams; integrating real per-animal
behavioural time series is left for future work. Evaluation episodes were also
sampled from the same preprocessed dataset as training rather than from a
separate temporally held-out period, so the reported estimates characterise
in-sample policy behaviour under a proof-of-concept simulation.


% ---------------------------------------------------------------------
% [5] Data availability statement -- replaces the placeholder about the
% repository URL/DOI (fill in once the repo is created).
% ---------------------------------------------------------------------
To support reproducibility, the source code, data-preprocessing scripts, model
configurations, random seeds, trained-model checkpoints, the reward-weight
sensitivity analysis and the figure-plotting scripts are provided in the
accompanying repository (see \texttt{reproducibility/}); the public GitHub URL
and the archived Zenodo DOI will be inserted upon acceptance.
